%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{jorge-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Jorge}{Verastegui}{ \urlstyle{same}
\href{mailto:jorge@verastegui.net}{jorge@verastegui.net} | +591-70513933 | \href{https://github.com/jorgeverastegui}{github.com/jorgeverastegui}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{San Pablo Catolic University}
\descript{Diploma in teacher training for higher education}
\location{2021 | Bolivia, La Paz }
\sectionsep

\subsection{San Andrés University}
\descript{Chemical Engineering}
\location{1993 | Bolivia, La Paz }
\sectionsep

\subsection{San Andrés University}
\descript{Msc in Control System Engineering}
\location{2003 | Bolivia, La Paz}
Pending thesis 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/jorgeverastegui}{\bf jorgeverastegui} \\
LinkedIn:// \href{https://www.linkedin.com/in/jorge-verastegui-9352259/}{jorge-verastegui-9352259/}\\
Twitter://  \href{https://twitter.com/jorge31284084}{\bf @jorge31284084} \\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Lenguage  SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Lenguage Skills}
\descript{English}
\location{Intermedium}
\sectionsep
\descript{Spanish}
\location{Native}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certifications}
\descript{Certified Kubernetes Adminitrator}
\location{Linux Fundation,2021}
\sectionsep
\descript{Certified System Adminitrator}
\location{Linux Fundation,2016}
\sectionsep
\descript{Digium-Certified Asterisk Professional}
\location{DCAP ,2011 Santiago de Chile}
\sectionsep
\descript{Cisco CCNA}
\location{La Paz, Boliva, 2001}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.63\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{OpenIt}
\descript{ | Engineering Consultant }
    \location{Fec. 2021 - Present | La Paz, Bolivia (remote) }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Informix admin support | Zimbra support | Proxmox support
\end{tightemize}    
\sectionsep

\runsubsection{AGETIC}
\descript{ | Chief of Development unit }
\location{Electronic Government and Information Technologies Agency}
\location{Aug. 2020 - Jan  2021| La Paz, Bolivia}
\begin{tightemize}
\item Agile development management 
\end{tightemize}    
\sectionsep


\runsubsection{VIRIDIAN}
\descript{ | Chief Research Officer}
\location{Nov. 2017 - Apr. 2020 | La Paz, Bolivia}
\begin{tightemize}
\item Microservices Architect
\item Java programming in financial systems
\item DevOps Engineer    
\end{tightemize}    
\sectionsep

\runsubsection{ABC}
\descript{ | Head of Technology and Information Systems}
\location{Bolivian highway administrator}
\location{Mar. 2016 - Sept. 2017 | La Paz, Bolivia}
\begin{tightemize}
\item Information Systems Management
\item Management, design and implementation of Linux Servers
\item Proxmox administration
\end{tightemize}    
\sectionsep

\runsubsection{VELANORMA}
\descript{ | General Manager}
\location{Nov. 2011 - Dec. 2016 | La Paz, Bolivia}
\begin{tightemize}
\item Application development (Java, AngularJs, Wicket)
\item Design and implementation of Linux Servers.
\item Design and implementation of IP telephony solutions
\end{tightemize}    
\sectionsep


\runsubsection{CETUS-GROUP S.R.L}
\descript{ | IT project manager}
\location{Apr. 2011 - Dec. 2015 | La Paz, Bolivia}
\begin{tightemize}
\item Design and implementation of Linux Servers.
\item Design and implementation of IP telephony solutions
\item Design and implementation of HTTP Servers, DNS, Email.
\end{tightemize}    
\sectionsep


\runsubsection{Several industrial companies}
\descript{ | IT professionl }
\location{Aug. 1996  - Mar. 2011 | La Paz, Bolivia}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical skills}
\descript{Network Protocols  and common services}
    \location {20 years - expert}
\descript{Linux Enviroments }
    \location{20 years - expert}
\descript{System Engineering and DevOps }
    \location{ 3 years - senior}
\descript{Scrum| Scrum Master | Project Owner }
    \location{3 years - senior}
\descript{ Project Manager | Leadership and desing }
    \location{3 year - senior} 
\descript{Programming}
    \location{Java \textbullet{}   Shell \textbullet{}  C \textbullet{} C++
    \textbullet{} JavaScript\\
    PostgreSQL \textbullet{} PHP \textbullet{} Mysql \textbullet{} \LaTeX\ }
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
